Digital History in Finland, 1488-1828

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png

selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)

@@

# Top publication places
ntop <- 10
top <- names(top(df, "publication_place", ntop))

>>>>

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)

@@

# Top publication places
ntop <- 10
library(bibliographica)
top <- names(top(df, "publication_place", ntop))

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("hautajaiset", "häät", "juhlamenot")
catalogue <- "Fennica"
df <- df.full # full time span
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
# Selected catalogue with selected topics
df <- df %>% filter(catalog == catalogue & hit)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)
}
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
df <- filter(df0, catalog == "Kungliga") %>%
      filter(publication_year <= 1828)

field <- "subject_topic"
entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))

df <- filter(df0, catalog == "Kungliga" & publication_place == "Uppsala") %>%
      filter(publication_year <= 1828)

>>>>

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("hautajaiset", "häät", "juhlamenot")
catalogue <- "Fennica"
df <- df.full # full time span
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
# Selected catalogue with selected topics
df <- df %>% filter(catalog == catalogue & hit)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub)) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
catalogue = "Kungliga"

df <- filter(df0, catalog == catalogue) %>%
      filter(publication_year <= 1828)

field <- "subject_topic"
entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
s <- write_xtable(entries, file = paste(output.folder, catalogue, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))

df <- filter(df0, catalog == catalogue & publication_place == "Uppsala") %>%
      filter(publication_year <= 1828)
